\textbf{CSDS 491: Assignment 4}

### 2021-04-22 A4/article.tex
🔨 Add reference for Exploration.

t-SNE runs in an iterative manner, as it will move one point at a time untill it reaches the stopping criteria (which is usually numbers of iterations). W.L.O.G., let's check out how will t-SNE move the \textcolor{red}{leftmost red} point:

>>>>

t-SNE runs in an iterative manner, as it will move one point at a time untill it reaches the stopping criteria (which is usually numbers of iterations). W.L.O.G., let's check out how will t-SNE move the \textcolor{red}{leftmost red} point (note the following plots are coming from \href{https://www.youtube.com/watch?v=NEaUSP4YerM}{StatQuest with Josh Starmer} with a little bit post-process for better representation in written media):
